### 2018-06-13 Sections/optimising_the_world.tex
More opt algs

\comment{Quantum optimisation algorithms}%https://en.wikipedia.org/wiki/Quantum_optimization_algorithms

@@

%\subsection{\textbf{BQP} optimisation problems}\index{\textbf{BQP} optimisation problems}

%The optimisation problems discussed until now have been satisfiability problems residing in \textbf{NP}-complete, limited to only quadratic quantum enhancement. Are there any other optimisation problems that natively reside in \textbf{BQP}, and therefore inherently offer exponential quantum speedup? There are, although the examples are far less ubiquitous than the plethora of satisfiability-based optimisation problems.

%\comment{To do!}

>>>>

The optimisation problems discussed until now have been satisfiability problems residing in \textbf{NP}-complete, limited to only quadratic quantum enhancement owing to their utilisation of Grover's algorithm. Are there any other optimisation problems to which quantum computers lend themselves, potentially with the cherished exponential enhancement. There are, although the examples are far less ubiquitous than the plethora of satisfiability-based optimisation problems.

\subsubsection{Least squares fitting}

A quantum-enhanced algorithm for performing least squares fitting\index{Least squares fitting} was described by \cite{HHL?}, potentially offering an exponential enhancement, depending on the sparsity of the data. As input it takes a set of data-points, \mbox{$(x_i,y_i)$}, and functions, $f_j$, outputting a set of coefficients, $\lambda_k$, defining a linear combination of those functions that fits the data, as well as a parameter characterising the quality of the fit. That is, we find the $\lambda$ that defines the fitting function\index{Fitting function},
\begin{align}
f_{\vec\lambda(x)} = \sum_k \lambda_k f_k(x),
\end{align}
such that the quality estimator\index{Quality estimator} is minimised following a sum-of-squares metric,
\begin{align}
E = \sum_i |f_{\vec\lambda}(x_i)-y_i|^2.	
\end{align}
This can be thought of as an optimisation problem in the sense that our goal is to find a linear combination of functions that maximises the fit quality. This problem finds widespread use across many fields, particularly in statistics.

\subsubsection{Semidefinite programming}

Semidefinite programming\index{Semidefinite programming} is a technique for finding solutions to constrained linear systems\index{Linear systems}. Although the technique is already classically efficient, running in polynomial time, a quantum-enhanced version has been described \cite{???}, which promises exponential speedup in certain parameter regimes.

\comment{To do}

@@
